Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-02-16 Scripts/Initial_Analysis.Rmd
Fixed figure 1

# Manually include rest of EEZs

cont_eez <- plot_data %>% 
  filter(level == "eez") %>% 
  slice(1:36) %>%
  select(-1) %>% 
  mutate(
    value = ifelse(metric == "per",100,232),
    taxon_emer = c(seq(2082,2099,1),seq(2082,2099,1))
  )

@@

# Percentage increase of EEZ after 2020
lm_eez <- plot_data %>% 
  filter(taxon_emer <= 2020,
         tresh == "tresh_one",
         metric == "per")

summary(lm(lm_eez$taxon_emer~lm_eez$value))

>>>>

# Manually include rest of data untill 2100
cont_eez <- plot_data %>% 
  filter(level == "eez") %>% 
  arrange(taxon_emer) %>% 
  slice(1:24) %>%
  select(-1) %>% 
  arrange(metric) %>% 
  mutate(
    value = ifelse(metric == "per",100,228),
    taxon_emer = c(seq(2088,2099,1),seq(2088,2099,1))
  )

@@
